Model LF

### 2023-03-18 paper version Hamid new test.Rmd
commit new wage equation

```{r}
## Creating the new shock variables
max_dp_shock= obs_dp_q
stat_reg_shock = ts(0.02, start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

```{r}
max_dp_test= TSLAG(obs_dp_q,4) +(stat_reg_q+stat_tilpas_q) * TSLAG(obs_dp_q,4) 
```

```{r}
wage_growth= TSDELTA(wage_ds,4)/TSLAG(wage_ds,4)
```

@@

```{r}
wage_ben_gap = (wage_ds - obs_dp_q)/obs_dp_q

wage_ben_gap_mean=ts(mean(wage_ben_gap),start = c(2005,2), end = c(2020,1), frequency = 4 ) 
wage_ben_gap_mean_test= ts(0.45,start = c(2005,2), end = c(2020,1), frequency = 4 )

wage_gap1 = (wage_ds*(1+inflation_t) - obs_dp_q)/obs_dp_q

## We can see that the actual wage gap observed in the data is below the desired wage gap, which means the worker unions demand a higher Target wage these years.2006, 2012, 2013,2014,2015,2016,2017

@@

D_2012_2017=create_dummy_ts(start_basic = c(2006, 2), end_basic=c(2020,1),
 dummy_start=c(2012,1), dummy_end = c(2017,4),
 basic_value = 0, dummy_value = 1, frequency = 4)

wage_ds_t_nu= ifelse(D_2012_2017>=1, obs_dp_q*(1+wage_ben_gap_mean), wage_ds_t) # I denne variable tager worker unions højde for gap mellem løn og max_dp, lignigne er ikke automatiseret så selv kig hhvornår den er over under gap!

alpha=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

max_dp_mova=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= alpha*wage_ds*(1+inflation_t) + (1-alpha)*max_dp_mova*(1+wage_ben_gap_mean)
IF> SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

COMMENT> 
IDENTITY> max_dp_mova
EQ> max_dp_mova = (TSLAG(max_dp,4) +TSLAG(max_dp,3)+ TSLAG(max_dp,2)+ TSLAG(max_dp,1))/4

COMMENT> 
IDENTITY> alpha
EQ> alpha = 1
IF> TSLAG(wage_gap1,0) >= wage_ben_gap_mean
IDENTITY> alpha
EQ> alpha = 0
IF> TSLAG(wage_gap1,0) < wage_ben_gap_mean

COMMENT> 
IDENTITY> wage_gap1
EQ> wage_gap1 = (wage_ds*(1+inflation) - max_dp_mova)/max_dp_mova

@@

COMMENT> 
BEHAVIORAL> wage_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(wage_ds) = p_522* TSDELTA(TSLAG(ur,1)) + p_523* TSDELTALOG(prod_ds)  + p_524* LOG(TSLAG(wage_ds,1)) + p_525* LOG(TSLAG(wage_ds_t,1)) + p_526* LOG(TSLAG(prod_ds,1))  + p_527 * (d_2009q1 + d_2009q2)
COEFF> p_522 p_523 p_524 p_525 p_526 p_527
STORE> coe(20)

@@

S_modelData=list(

@@

  max_dp_shock = TIMESERIES(c(max_dp_shock),   
                       START=c(2005,2),FREQ=4),
  part1 = TIMESERIES(c(part1),   
                       START=c(2005,2),FREQ=4),

@@

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4),
   alpha = TIMESERIES(c(alpha),   
                       START=c(2005,2),FREQ=4),
  wage_ben_gap_mean = TIMESERIES(c(wage_ben_gap_mean),   
                       START=c(2005,2),FREQ=4),
  max_dp_mova = TIMESERIES(c(max_dp_mova),   
                       START=c(2005,2),FREQ=4)
  )
```

@@

S_modelData$max_dp_mova = max_dp_mova

@@

plot(window((inflation_01 - inflation_bs1), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window((max_dp_01 - max_dp_bs1), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(max_dp_bs1)

alpha_01-alpha_bs1

plot(window(wage_gap1_bs1-wage_ben_gap, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1", ylim= c(-0.09,0.03));
lines(window((wage_gap1_01-wage_ben_gap), start= 2014), col= "green", lwd=2);
legend("left", legend=c("Wages"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

>>>>

```{r}
## Creating the new shock variables

stat_reg_shock = ts(0.02, start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

```{r}
max_dp_test= TSLAG(obs_dp_q,4) +(stat_reg_q+stat_tilpas_q) * TSLAG(obs_dp_q,4)

max_dp_test-obs_dp_q
```

@@

@@

library(dynlm)
library(sandwich)

log_wage <- log(wage_ds1)
log_wage_diff <-diff(log_wage)
ur_diff <- diff(ur)
log_prod <-log(prod_ds)
log_prod_diff <- diff(log_prod)
log_wage_t <- log(wage_ds_t)
test= obs_dp_q-wage_ds1
dummy=d_2009q1 + d_2009q2

wage_reg=dynlm(log_wage_diff~1+  L(log_wage_diff,2)  +L(ur_diff,1) + log_prod_diff + L(diff(test), 2) + L(log_wage,1) + L(log_wage_t,1) + L(log_prod,1) + I(d_2009q1 + d_2009q2), start = c(2006,3))

coeftest(wage_reg, vcov= vcovHC, type="HC0")

summary(wage_reg)

shapiro.test(residuals(wage_reg))

```{r}
wage_gap1=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4 )
```

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

@@

COMMENT> 
BEHAVIORAL> wage_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(wage_ds) =p_520 + p_521*TSDELTALOG(TSLAG(wage_ds,2)) + p_522* TSDELTA(TSLAG(ur,1)) + p_523* TSDELTALOG(prod_ds)+ p_527* TSDELTA(TSLAG(max_dp-wage_ds,2))+ p_524* LOG(TSLAG(wage_ds,1)) +  p_525* LOG(TSLAG(wage_ds_t,1)) + p_526* LOG(TSLAG(prod_ds,1)) + p_528*dummy
COEFF> p_520 p_521 p_522 p_523 p_527 p_524 p_525 p_526 p_528
STORE> coe(20)

@@

S_modelData=list(
  dummy = TIMESERIES(c(dummy),   
                       START=c(2005,2),FREQ=4),

@@

  part1 = TIMESERIES(c(part1),   
                       START=c(2005,2),FREQ=4),

@@

  shock_wage_ds_model  = TIMESERIES(c(shock_wage_ds_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4),
  emp_old = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
  emp_sens = TIMESERIES(c(emp),   
                        START=c(2005,2),FREQ=4),
   prod_ds_sens = TIMESERIES(c(prod_ds),   
                        START=c(2005,2),FREQ=4),
    xk_ds_used = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  xk_ds_disc = TIMESERIES(c(xk_ds),   
                        START=c(2005,2),FREQ=4),
  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens_3 = TIMESERIES(c(sens_3),   
                       START=c(2005,2),FREQ=4),
  disc = TIMESERIES(c(disc),   
                       START=c(2005,2),FREQ=4)
  )
```

@@

S_modelData$dummy = dummy

@@
